---
title: "homework04"
author: "Adrian Wiegman"
date: "February 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Suppose x = 1.1, a = 2.2, and b = 3.3. Assign each expression to the value of the variable z and print the value stored in z.
```{r}
X <- 1.1
a <- 2.2
b <- 3.3
z <- vector(length=4)
z[1] <- X^a^b
z[2] <- (X^a)^b
z[3] <- 3*X^3 + 2*X^2 + 1
z[4] <- floor(10*(z[3] - floor(z[3]))) 
names(z) <- letters[seq_along(z)]
#floor(x) gives the left most digit in x
#for example: if x = 3.5 floor(x) = 3 
for (i in seq_along(z)){print(z[i])}
```
- A. $$ z = x^{a^{b}} = $$ `r z['a']`
- B. $$ z = (x^a)^b = $$  `r z['b']`
- C. $$z = 3x^3 + 2x^2 + 1 = $$ `r z['c']`
- D. second digit in z, C. = `r z['d']`

2. Using the rep and seq functions, create the following vectors:
```{r}
a <- c(seq(from=1,to=8),seq(7,1))
print(a)
b <- rep(x=1:5,times=1:5)
print(b)
c <- rep(x=5:1,times=1:5)
print(c)
```

3. Create a vector of two random uniform numbers. In a spatial map, these can be interpreted as x and y coordinates that give the location of an individual (such as a marked forest tree in a plot that has been mapped). Using one of R’s inverse trigonometry functions (asin(), acos(), or atan()), convert these numbers into polar coordinates (If you don’t know what polar coordinates are, read about them on the web or in your calculus textbook).
```{r}
set.seed(10)
z <- runif(2)
print(z) # z[1] is x and z[2] is y
names(xyCoords) <- c('x','y')
xyCoords <- z
radius <- sqrt(z[1]^2 + z[2]^2) #pythagorian theorum
print(radius)
theta <- atan2(x=z[1],y=z[2]) #using arctan2 to convert x,y to an angle
theta <- acos(z[1]/radius) #using arcsin of (x/radius) produces theta relative to 0,1
atan2(x=z[1],y=z[2])/theta 
atan2(x=z[1],y=z[2])/theta == 1 #check that these equations are equal
#something is wrong with this test, the value is 1 but the test gives FALSE
print(theta*360/(2*pi)) #radians to degrees
polarCoords <- c(radius,theta) #radians
names(polarCoords) <- c('radius','theta')
```

randomly generated x,y coordinates $(x,y):$ 
```{r} 
print(xyCoords)
```
`r in lin`
to convert x,y coordinates to polar coordinates (radius,angle), the radius, $r$, is calculated by calculating the length of the hypotenus of vector x,y using pythagarian theorum:
$$r = \sqrt{x^2+y^2}$$

then the angle or theta, $\theta$, can be caclulated using triganometric functions, e.g.: 
$\theta = \arctan{(r/x)}$ or $\theta = \arctan_2{(x,y)}$

the results below are n dimension polar coordinates generated from the x,y values above, r is between 0 and 1, $\theta$ is in radians:
$(r,\theta)$ `r print(polarCoords)`
to convert from radians to degrees multiply $\theta$ by $360/2\pi$


