---
title: "BeamerPres"
author: "Adrian Wiegman"
date: "January 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "FirstBeamerPrez"
author: "LaurenBomeisl"
date: "1/30/2018"
output: 
  beamer_presentation: 
    colortheme: beaver
    incremental: yes
    theme: Madrid
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slide Title

Add your markdown text

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## First Slide

- First Incremental bullet point
- Second
- Third

## Third Slide

>-first simultaneous bullet point
>-second simultaneous bullet point
>-third simultaneous bullet point

%comment

##Let's see some R

```{r, echo=FALSE}
library(ggplot1)
var1 <- runif(10)
var2 <- runif(10)
qplot(x=var1, y=var2)
```
## Slide with Plot

## Colored Bullet POints
>- Collection Mode
>- \color{grey} spatial and temporal
>- \color{red} taxonomic bias
>- \color{grey} sampling
>- more stuff

##Insert an Image
\begin{picture}(320,250)
\put(80,80){\includegraphics[height=6cm]} 


