---
title: "Dissertation Trajectories"
author: "Adrian Wiegman"
date: "February 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(DiagrammeR)
#http://rich-iannone.github.io/DiagrammeR/graphviz_and_mermaid.html
```

## Objectives
This document outlines the trajectories that my dissertation could take based on potential funding scenarios. At this time, two major proposals could influence my research: 

1. The North East SARE (**NE-SARE**): "Quantifying phosphorus retention in restored riparian wetlands of the Lake Champlain Basin"*

2. The Lake Champlain Basin Foundation (**LCBP**): "Synergistic use of recycled household and community nutrients to deliver balanced fertilization in Northeast agriculture"*

The major research outcomes of the LCBP proposal are data on phosphorus (P) pools and fluxes from three wetland sites, functional relationships between these fluxes and site characterstics, a hydrologic model, a riparian P model. These will be used to estimate P retention and export from three wetland sites. 

The major research outcomes of the NE-SARE proposal are Maize Yield, Soil Characterstics, Nutrient Leaching, and Life Cycle cost, energy, and greenhouse gas inventories for 7 recipes of recycled organic fertilizers. In addition farmer surveys will be conducted and will indicate the likelyhood of adoption of the 7 seven fertilizer blends. 

Together data from the LCBP and the NE-SARE grants can be used to estimate the impact of organics recycling and ecosystem restoration have on phosphorus loads to lake champlain and the associated cost of management.
 
There are four possible funding scenarios: 

1. Both LCBP and NE_SARE are awarded

2. LCBP is awarded and NE_SARE is not

3. NE-SARE is awarded and LCBP is not

4. Neither funding proposal is awared

Below I propose chapter organizations for my dissteration based on scenarios 1-3

## Scenario 1 - LCBP and NE-SARE are Funded
```{r, echo=FALSE}
grViz("
digraph boxes_and_circles{
  # a 'graph' statement
  graph [overlap = true, rankdir=TB, fontsize = 10]
  #External Data nodes
  node [shape = diamond,
        fontname = Helvetica]
  D1[label = 'EcoInvent Data']#diamond
  D2[label = 'USGS DEMs & Stream Guages']#diamond
  D3[label = 'Spatial Data'] #diamond

  # Funded Project nodes
  node [shape = circle,
        fontname = Helvetica]
  A [label = 'NE-SARE'] #Circle
  B[label = 'LCBP'] #Circle

  #Output Data nodes
  node [shape = box,
        fontname = Helvetica]
  A1[label = 'GHG Emissions'] 
  A3[label = 'Maize Yield'] 
  A2[label = 'Nutrient Leaching'] 
  B2[label = 'P Dynamics Functions']
  B3[label = 'P Pools and Fluxes']
  B1[label = 'Wetland P Retention/Export']
  
  #Output Model nodes
  node [shape = egg,
        fontname = Helvetica]
  A4[label = 'Org. Fertilizer LCA'] #Egg
  B5[label = 'Riparian P Model']#Egg
  B4[label = 'Hydrologic Model']#Egg
  M2[label = 'Watershed P Model']#egg
  M3[label = 'Water Quality Optimization']#egg
  
  #Chapter nodes
  node [shape = box, style = filled, fillcolor = yellow,
        fontname = Helvetica]
  C1[label = 'Chapter 1']
  C2[label = 'Chapter 2']
  C3[label = 'Chapter 3']
  C4[label = 'Chapter 4']

  #edge statements
  # NE_SARE data flows
  D1 -> A4
  A -> A1 
  A -> A3
  A -> A2
  A1 -> A4
  A3 -> A4
  A2 -> A4
  # LCBP data flows
  D2 -> B4
  B -> B2
  B -> B3
  B -> B4
  B2 -> B5
  B3 -> B5
  B4 -> B1
  B5 -> B1
  B2 -> C1
  B3 -> C1
  B5 -> C2
  D3 -> M2
  # Watershed Model data flows 
  A2 -> M2
  B1 -> M2
  M2 -> C3
  A4 -> M3
  M2 -> M3
  M3 -> C4
}
")
```

## Scenario 2 - Only LCBP is funded 
```{r, echo=FALSE}
grViz("
digraph boxes_and_circles{
  # a 'graph' statement
  graph [overlap = true, rankdir=TB, fontsize = 10]
  #External Data nodes
  node [shape = diamond,
        fontname = Helvetica]
  D1[label = 'EcoInvent Data']#diamond
  D2[label = 'USGS DEMs & Stream Guages']#diamond
  D3[label = 'Spatial Data'] #diamond

  # Funded Project nodes
  node [shape = circle,
        fontname = Helvetica]
  A [label = 'NE-SARE'] #Circle
  B[label = 'LCBP'] #Circle

  #Output Data nodes
  node [shape = box,
        fontname = Helvetica]
  A1[label = 'GHG Emissions'] 
  A3[label = 'Maize Yield'] 
  A2[label = 'Nutrient Leaching'] 
  B2[label = 'P Dynamics Functions']
  B3[label = 'P Pools and Fluxes']
  B1[label = 'Wetland P Retention/Export']
  
  #Output Model nodes
  node [shape = egg,
        fontname = Helvetica]
  A4[label = 'Org. Fertilizer LCA'] #Egg
  B5[label = 'Riparian P Model']#Egg
  B4[label = 'Hydrologic Model']#Egg
  M2[label = 'Watershed P Model']#egg
  M3[label = 'Water Quality Optimization']#egg
  
  #Chapter nodes
  node [shape = box, style = filled, fillcolor = yellow,
        fontname = Helvetica]
  C1[label = 'Chapter 1']
  C2[label = 'Chapter 2']
  C3[label = 'Chapter 3']
  C4[label = 'Chapter 4']

  #edge statements
  # LCBP data flows
  D2 -> B4
  B -> B2
  B -> B3
  B -> B4
  B2 -> B5
  B3 -> B5
  B4 -> B1
  B5 -> B1
  B2 -> C1
  B3 -> C1
  B5 -> C2
  D3 -> M2
  # Watershed Model data flows 
  A2 -> M2
  B1 -> M2
  M2 -> C3
  A4 -> M3
  M2 -> M3
  M3 -> C4
}
")
```

## Scenario 3 - Only NE-SARE is funded 
```{r, echo=FALSE}
grViz("
digraph boxes_and_circles{
  # a 'graph' statement
  graph [overlap = true, rankdir=TB, fontsize = 10]
  #External Data nodes
  node [shape = diamond,
        fontname = Helvetica]
  D1[label = 'EcoInvent Data']#diamond
  D2[label = 'USGS DEMs & Stream Guages']#diamond
  D3[label = 'Spatial Data'] #diamond

  # Funded Project nodes
  node [shape = circle,
        fontname = Helvetica]
  A [label = 'NE-SARE'] #Circle
  B[label = 'LCBP'] #Circle

  #Output Data nodes
  node [shape = box,
        fontname = Helvetica]
  A1[label = 'GHG Emissions'] 
  A3[label = 'Maize Yield'] 
  A2[label = 'Nutrient Leaching'] 
  B2[label = 'P Dynamics Functions']
  B3[label = 'P Pools and Fluxes']
  B1[label = 'Wetland P Retention/Export']
  
  #Output Model nodes
  node [shape = egg,
        fontname = Helvetica]
  A4[label = 'Org. Fertilizer LCA'] #Egg
  B5[label = 'Riparian P Model']#Egg
  B4[label = 'Hydrologic Model']#Egg
  M2[label = 'Watershed P Model']#egg
  M3[label = 'Water Quality Optimization']#egg
  
  #Chapter nodes
  node [shape = box, style = filled, fillcolor = yellow,
        fontname = Helvetica]
  C1[label = 'Chapter 1']
  C2[label = 'Chapter 2']
  C3[label = 'Chapter 3']
  C4[label = 'Chapter 4']

  #edge statements
  # NE_SARE data flows
  D1 -> A4
  A -> A1 
  A -> A3
  A -> A2
  A1 -> A4
  A3 -> A4
  A2 -> A4

  # Watershed Model data flows 
  A2 -> M2
  B1 -> M2
  M2 -> C3
  A4 -> M3
  M2 -> M3
  M3 -> C4
}
")
```