---
title: "Lecture 3"
author: "Adrian Wiegman"
date: "January 25, 2018"
output: 
  html_document: 
    css: C:/Program Files/Typora/resources/app/style/themes/github.css
    keep_md: yes
    theme: spacelab
---


```{r setup, include=FALSE}
#local R code chunks options are controlled above 
#knitr global options are controlled below
knitr::opts_chunk$set(echo = FALSE)
```

## More LaTex Tricks

### Summation
$$\sum_{i=1}^S{n_i}=N$$

### Sentence text

$$p(\mbox{occurance of species X})=0.67$$

### What about printing a backslash

$$\backslash a \le b \backslash$$

Rendering code of \LaTeX

using "ctrl alt i" creates an R code chunk

`echo=TRUE` prints the R code in the html, FALSE hides the R code
`eval=FALSE` prevents a code from executing
`message=FALSE`
```{r,echo=FALSE} 
library(ggplot2)
waterTemp <-runif(50) # cammel hump cammelHump naming convention
planktonAbun <- runif(50)
# qplot does not require a dataframe
qplot(x=waterTemp, y=planktonAbun)
# assigning x and y equal sign 
# print(waterTemp) #print statement
# head(waterTemp) # prints first six elements of a vector
# use "ctrl shift c" to insert/remove # before selected lines
```
Now we can add text here, say anything we want, etc. in the new chunk belo has access to the memory from all the chunks above. 
```{r, echo=TRUE,eval=TRUE,message=FALSE}
qplot(x=waterTemp)
```


